systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-06-30 paper/trunk/systemfit_code.tex
modifications, because lrtest.systemfit is now a wrapper function to lrtest.default
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@742 591db2bd-e0a0-4d22-8c19-2192dbb7da31
corrected a small typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@749 591db2bd-e0a0-4d22-8c19-2192dbb7da31
revised section about source code of systemfit (mainly changes due to modifications of the systemfit package)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@767 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The most important function in the \pkg{systemfit} package
is called \code{systemfit}.
It can be used to estimate systems of linear equations
by several different estimation methods.
Furthermore, this package provides some methods
to test hypotheses
(\code{ftest}, \code{wald\-test},
\code{lrtest}, \code{hausman}),
to extract the estimated coefficients (\code{coef})
and to calculate predicted values (\code{predict}).

@@

The \code{systemfit} function returns many objects
that users might be interested in.
A complete list is available in the documentation of this function
that is included in the package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical tests}
This section explains the implementation of the statistical tests described in
sections~\ref{sec:testingRestrictions} and~\ref{sec:hausman}.
The method \code{linear.hypothesis.systemfit}
can be used to test linear restrictions on the estimated parameters
by an $F$ test or a Wald/$\chi^2$ test.
Internally, the $F$ statistic is computed by the hidden function
\code{.ftest.systemfit}
and the Wald/$\chi^2$ statistic is computed by the method
\code{linear.hypothesis.default} of the \pkg{car} package.
The function \code{lrtest.systemfit}
computes the Likelihood-ratio (LR) test statistic.
On the other hand, the function \code{hausman.systemfit}
tests the consistency of the 3SLS estimator.
All functions return the empirical test statistic,
the degree(s) of freedom, and the $p$ value.

>>>>

The most important function in the \pkg{systemfit} package
is called \code{systemfit}.
It can be used to estimate systems of linear equations
by several different estimation methods.
Furthermore, this package provides methods
to test hypotheses
(\code{linear.hypothesis},
\code{lrtest}, \code{hausman}\hspace{0pt}\code{.systemfit}),
to calculate summary results (\code{summary}),
to print (summary) results (\code{print})
and to calculate predicted values (\code{predict}).
Moreover, there are several methods to extract
the estimated coefficients (\code{coef}),
their covariance matrix (\code{vcov}),
the fitted values (\code{fitted}),
the residuals (\code{residuals}),
the formula(s) (\code{formula}),
the model terms (\code{terms}),
the model frame (\code{model.frame}),
the model matrix (\code{model.matrix}),
and the log likelihood value (\code{logLik}).
There does not exist a special method to extract
the degrees of freedom of the residuals from \code{systemfit} objects,
because the default method of \code{df.residual}
works for these objects.

@@

The \code{systemfit} function returns an object of class \code{systemfit}
that contains many elements users might be interested in.
A complete description is available in the documentation of this function
that is included in the package.
A comparison with the elements returned by \code{lm},
the basic tool for linear regressions in \proglang{R},
is available in appendix~\ref{sec:returned-object}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical tests}
This section explains the implementation of the statistical tests described in
sections~\ref{sec:testingRestrictions} and~\ref{sec:hausman}.
The method \code{linear.hypothesis.systemfit}
can be used to test linear restrictions on the estimated parameters
by an $F$ test or a Wald/$\chi^2$ test.
Internally, the $F$ statistic is computed by the hidden function
\code{.ftest.systemfit}
and the Wald/$\chi^2$ statistic is computed by the method
\code{linear.hypothesis.default} of the \pkg{car} package
\citep{r-car-1.2-1}.
The method \code{lrtest.systemfit} is a wrapper function
to \code{lrtest.default} of the \pkg{lmtest} package
\citep{r-lmtest},
which computes the Likelihood-ratio (LR) test statistic.
All these functions return an object of class \code{anova}
that contains --- amongst others ---
the empirical test statistic, the degrees of freedom,
and the corresponding $p$ value.

The function \code{hausman.systemfit}
tests the consistency of the 3SLS estimator.
It returns an object of class \code{htest},
which contains --- amongst others ---
the empirical test statistic,
the degrees of freedom, and the $p$ value.
